### 2024-10-08 sections/projects.tex
Update projects.tex

\begin{cvhonors}
\cvhonor
{Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), Resarch Associate (Ximena Orchard, Principal Investigator), about USD\$4 000. Period: 2019.} %% {\pounds} 3 000
{UAH}
{2019}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), Research Associate (Ximena Orchard, Principal Investigator), about USD\$4 000. Period: 2019.} %% {\pounds} 3 000
{UAH}
{2019}
\end{cvhonors}
